Evaluating a simplified forecast model in comparison to the ECDC forecasting hub ensemble

### 2022-06-07 docs/paper/paper.Rmd
more plot tuning

```{r make-rwis-plots}
plot_rwis_horizon <- relative_wis |>
  copy() |>
  DT(, horizon := fct_rev(as.factor(horizon))) |>
  plot_relative_wis(
    y = horizon, fill = horizon
  ) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  labs(y = "Forecast horizon (weeks)") +
  guides(fill = guide_none(), point_color = guide_none(), point = guide_none())

plot_rwis_location <- relative_wis |>
  DT(horizon == 1 | horizon == 4) |>
  DT(, horizon := fct_rev(as.factor(horizon))) |>
  plot_relative_wis(
    y = location_name, fill = horizon, alpha = 0.3,
    jittered_points = FALSE, quantiles = NULL,  point_color = horizon
  ) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  labs(
    y = "Forecast location", fill = "Forecast horizon (weeks)",
    point_color = "Forecast horizon (weeks)"
  )

@@

```{r assemble-eval, fig.height = 12, fig.width = 12, out.width = "95%"}
 (
  (
    (
      plot_rwis_horizon / plot_rwis_by_month
    )  +
    plot_layout(heights = c(4, 5), guides = "collect")
  ) |
  plot_rwis_location + guides(fill = guide_none())
) +
  plot_layout(guides = "collect", widths = c(1, 1)) +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre"
  )
```

@@

```{r plot-coverage, fig.height = 12, fig.width = 18, out.width = "95%"}
 (
  (
    (
      plot_coverage_range(coverage, ranges) /
      plot_rel_score_by_quantile(relative_interval_score)
    )  +
    plot_layout(heights = c(3, 1), guides = "collect")
  ) |
  plot_coverage_quantiles(scores)
) +
  plot_layout(guides = "collect", widths = c(1, 2)) +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre"
  )
```

>>>>

```{r make-rwis-plots}
plot_rwis_horizon <- relative_wis |>
  copy() |>
  DT(, horizon := fct_rev(as.factor(horizon))) |>
  plot_relative_wis(
    y = horizon, fill = horizon,
  ) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  labs(y = "Forecast horizon (weeks)") +
  guides(fill = guide_none(), point_color = guide_none(), point = guide_none())

plot_rwis_location <- relative_wis |>
  DT(horizon == 1 | horizon == 4) |>
  plot_relative_wis(
    y = location_name, fill = as.factor(horizon), alpha = 0.3,
    jittered_points = FALSE, quantiles = NULL,  point_color = horizon
  ) +
  scale_fill_brewer(palette = "Dark2") +
  scale_color_brewer(palette = "Dark2") +
  labs(
    y = "Forecast location", fill = "Forecast horizon (weeks)",
    point_color = "Forecast horizon (weeks)"
  )

@@

```{r assemble-eval, fig.height = 12, fig.width = 12, out.width = "95%"}
 (
  (
    (
      plot_rwis_horizon / plot_rwis_by_month
    )  +
    plot_layout(heights = c(4, 5), guides = "collect")
  ) |
  plot_rwis_location
) +
  plot_layout(guides = "collect", widths = c(1, 1)) +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre"
  )
```

@@

```{r plot-coverage, fig.height = 12, fig.width = 18, out.width = "95%"}
 (
  (
    (
      plot_coverage_range(coverage, ranges) /
      plot_rel_score_by_quantile(relative_interval_score)
    )  +
    plot_layout(heights = c(3, 1), guides = "collect")
  ) |
  plot_coverage_quantiles(scores)
) +
  plot_layout(widths = c(1, 2), guides = "collect") +
  plot_annotation(tag_levels = "a") &
  theme(
    legend.position = "bottom", legend.margin = margin(),
    legend.justification = "centre"
  )
```
